Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-19 review_article.Rmd
inetractive graphics references

# Cartograms and other spatially warped displays {#ch:alternatives}

@@

@@

>>>>

# Alternatives to choropleth maps {#ch:alternatives}

## Micromaps
XXX Something needs to be said about micromaps https://cran.r-project.org/web/packages/micromapST/vignettes/JSSmicromapSTv63i03.pdf

@@

XXX Define interactivity, and also animation

@@

- the arcGIS standard https://pro.arcgis.com/en/pro-app/help/mapping/animation/overview-of-animation.htm
- very general infovis reference that refers to Buja, Cook, Swayne distinguishing between direct manipulation and interactive graphics https://hal.inria.fr/tel-01096366/file/VA2_PERIN_CHARLES_17112014.pdf
- explanation of inetractivity and direct manipulation: https://books.google.com.au/books?id=A6TMqxkW-EoC&pg=PA6&lpg=PA6&dq=direct+manipulation+%22swayne%22+%22klinke%22&source=bl&ots=tXYKP8JbbV&sig=ACfU3U3KhN-_YNt_UV5SmThsl4D2gY9A4g&hl=en&sa=X&ved=2ahUKEwj6u9vgqtzkAhVKeysKHQ6iByUQ6AEwA3oECAgQAQ#v=onepage&q=direct%20manipulation%20%22swayne%22%20%22klinke%22&f=false
- might be useful to look at https://towardsdatascience.com/a-complete-guide-to-an-interactive-geographical-map-using-python-f4c5197e23e0
- a classic http://www.cs.umd.edu/hcil/trs/2001-08/2001-08.html
- this is one reference that maybe yoou have missed: https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf
